\section{Broader Impacts: Education and Outreach}
\label{sec:impact}

\PP{Leadership in undergraduate education.}
Both PI Min and PI Kim, although juniors, are passionate
educators. For example, in two courses taught in the last year, 
PI Kim got a student evaluation rating of 4.7/5.0 in CS 6265 (Information Security Lab, Fall 2016)
and 4.8/5.0 in CS3210 (Design Operating Systems, Spring 2016),
from 30 and 40 graduate and undergraduate students, respectively.
%
In the past, PI Kim successfully led a few curriculum development efforts
at Georgia Tech, supported by NSF, Intel, and Georgia Tech. In particular,
he designed a new curriculum to educate
the next-generation of security analysts,
handling a large amount of data
by using massively parallel and scalable systems.
%
With profiling tools developed as part of this project, 
PI Min and PI Kim will design new course and lab materials
that introduce (1) how to debug scalability problems of
large data processing programs (e.g., Spark)
and (2) how to resolve and validate the scalability problems
based on the quantified insights with our tools.

\squishlist
\item SaTC-EDU: EAGER: Big Data and Security: Educating The Next-Generation Security Analysts (2015)
\item Intel/NSF: Integrating Security Concepts in an Undergraduate CS Curriculum (2014, 2015)
\item GT-Fire: New Curriculum Development for Secure Big Data Processing (2015)
\squishend

\PP{Outreach to undergraduates, women, and minorities.}
The University System of Georgia (USG) recently started an ambitious
effort to increase the cyber security workforce
across all units of the USG system (29 campuses). 
%
These include multiple HBCUs, such as Spelman and Morehouse
Colleges, as well as research universities.
%
Georgia Tech is expected to play a leading role in developing effective
programs that deploy cyber security content to a diverse set of programs.
%
PI Kim will lead the development of a systems security curriculum,
called the ``Educating the Educators'' program
and introduce our profiling tools to develop
security applications, such as a data-driven policy auditor.

\PP{Outreach to the research and development community.}
The two PIs are active contributors to the open source community.
For example, their group was invited to the 2015 Linux
Plumbers Conference to present another open source project that
enables rebootless kernel updates.
%
The two PIs previously contributed to Linux kernel, Android, Chrome,
Firefox, OpenSSL, Python, PHP, QEMU, etc. In particular, all of PI
Kim's research projects have been publicly maintained, and some of
them, such as \href{https://github.com/tsgates/mbox}{MBox}
and \href{https://github.com/sslab-gatech/opensgx}{OpenSGX},
have gained significant popularity.
%
To foster successful deployment and contribution to the
community, technical reports, and software artifacts developed through
this proposed work will be publicly available.

\looseness=-1
