\section{Results From Prior NSF Support}
\label{sec:prior}

{\bf Changwoo Min} has not had any NSF support in the last five years.

\vspace{5px}
\noindent{\bf Taesoo Kim}
has received four prior NSF awards (three as PI and one as
co-PI). The two most recent awards are listed as follows:
\vspace{5px}

\noindent\emph{``TWC: Medium: Collaborative: Systems, Tools, and
  Techniques for Executing, Managing, and Securing SGX Programs''}
(NSF CNS 1563848, 06/2016--05/2020, \$671,776).

\textit{Intellectual Merit}: The project develops
design principles to build secure SGX programs
that run on a hostile computing environment
where their underlying OS, hypervisor and firmware
can be potentially malicious.
%
\textit{Broader Impacts}: The project delivers
open source toolchain and systematization of knowledge
on secure SGX programming patterns
to enhance the security of system software.

\vspace{5px}
\noindent \emph{``CI-P: Collaborative: A Community-Driven Open
  Research Infrastructure for Intel SGX''}
(NSF CRI 1629851, \$50,000, 08/2016--07/2017).

\textit{Intellectual Merit}: The project 
develops an open source infrastructure for SGX research
that includes libraries and operating system support.
%
\textit{Broader Impacts:}
The project
leads the community efforts in fostering the adoption
of Intel SGX in a secure, community-driven fashion.

% \emph{``Georgia Tech's Scholarship-for-Service (SFS) Program''}
% (NSF SFS 1565523, \$4,999,196, 09/2016--09/2021).

% \emph{``SaTC-EDU: EAGER: Big Data and Security: Educating The Next-Generation Security Analysts''} 
% (NSF DGE 1500084, 06/2016--05/2018, \$300,000).
% %
% \textbf{Intellectual Merit}:
% the identification of a set
% of basic principles and effective techniques of applying data analysis
% to security education, and the contribution to research and
% practice in data analysis and security.
% %
% \textbf{Broader Impacts}:
% newly designed, developed, and
% evaluated publicly available resources such as lab materials for
% teaching data-driven security analysts, as well as the training of
% better technical quality of security analysts.

% \vspace{5px}
% All software artifacts, education materials, and experiment results
% of the PI's research projects supported by the NSF
% are publicly available in code repositories
% at \url{https://github.com/sslab-gatech}.
