\section{Results From Prior NSF Support}
\label{sec:prior}

\kim has been a PI of
\emph{``SaTC-EDU: EAGER: Big Data and Security: Educating The
  Next-Generation Security Analysts''} (NSF DGE 1500084, 06/2016-05/2018, \$300,000).

\if 0
\PP{Award information.}
The intellectual merit is the development of course modules and lab materials
that integrate data analysis and security
for the education of next-generation security analysts.
The broader impact is the
dissemination of these new teaching materials and sharing of lessons
learned, in addition to the training of a new generation of security
analysts.
%
This funding results in course materials and lab practices
for ``Information Security Lab (CS 6265)''
that the PI plans to provide in Fall 2015.
\fi

\PP{Intellectual merit.}
It is challenging to educate security analysts. 
The education requires the instructors' deep understanding of two distinct areas: 
data analysis and security. More importantly, the consolidation of these two 
areas must be carried out from the design of the education to the interaction 
during the education. 

%
Based on our team's extensive experience in data analysis and
security, we will identify a set of basic principles and effective 
techniques of applying data analysis to security, upon which the education is 
designed.
%
This project will not only serve the
education needs but also contribute to research and practice in
data analysis and security.

\PP{Broader impacts.}
The newly designed, developed and evaluated
resources such as lab materials
for teaching data-driven security analysts
will be available to the public as online modules
so that the educational community can adopt the approach.
%
We believe this effort will result in increasing numbers as well as better 
technical quality of security analysts. The government and related industries 
will therefore benefit from more effective practice in securing cyberspace.
